Network Configuration Synthesis with Abstract Topologies

### 2016-11-07 paper/abstraction/appendix.tex
update substitution proof

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
     ~~~~~ \{ l \rightarrow rc ~\vert \\
     ~~~~~~~~~ l \in internal(V) \\
     ~~~~~~~~~ m = (l,q_m) \in PG, \\
     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\

     ~~~~~ \}
  \end{array} \]%

@@

  \caption{Simplified BGP syntax.}
  \label{fig:abgp-syntax}
\end{figure}%

@@

>>>>

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& ps_1 \rightarrow {pc}_1, ~\dots,~ ps_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (ps_1,PG_1,ord_1), \dots, (ps_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ ps_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

@@

  \caption{BGP syntax and compilation.}
  \label{fig:abgp-syntax}
\end{figure}%

@@

\subsection{Substitution}

\begin{defn}
  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
\end{defn}

\begin{thm}
  $con(compile_{ABGP}(compile_{PG}(pol))) = compile_{ABGP}(compile_{PG}(con(pol)))$

    We know from the previous theorems and the definition of concretization, we have the following:

    \[ \begin{array}{lll}
       (t_1, PG^A_1, ord^A_1), \dots, (t_k,PG^A_k,ord^A_k)    &=& compile_{PG}(pol) \\
       (\Gamma(t1), PG_1, ord_1), \dots, (\Gamma(t_k),PG_k,ord_k)  &=& compile_{PG}(con(pol)) \\
    \end{array} \]%

    where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$.

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (\Gamma(t_1),PG_1,ord_1), \dots, (\Gamma(t_k),PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ \Gamma(t_i) \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(M) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG_i,m) \} \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord_i(f(m)) : (in,q_n) \rightarrow (out,q_m) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = con(\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = con(ord^A_i(M) : (in,q_n) \rightarrow (out,q_M)) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ pfx \rightarrow con(ma) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ con(\bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \}) \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l' \rightarrow rc ~\vert~ con(rc) = \\
     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

  \[ \begin{array}{l}
     con(\textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
  \end{array} \]%
